Evaluating a simplified forecast model in comparison to the European forecasting hub ensemble

### 2022-10-11 paper/paper.Rmd
fix bug in labels

relative_ae_by_horizon <- scores |>
  summarise_scores(by = c("horizon", "model")) |>
  DT(, interval_score := ae_median) |>
  calc_relative_score(cols = c("horizon")) |>
  DT(, ris := round(relative_interval_score, 2)) |>
  DT(, interval_score := NULL)
setnames(
  relative_ae_by_horizon, c("relative_interval_score", "ris"),
  c("Absolute error of the median", "raem")
)

>>>>

relative_ae_by_horizon <- scores |>
  summarise_scores(by = c("horizon", "model")) |>
  DT(, interval_score := ae_median) |>
  calc_relative_score(cols = c("horizon")) |>
  DT(, ris := round(relative_interval_score, 2)) |>
  DT(, interval_score := NULL)
setnames(
  relative_ae_by_horizon, c("relative_interval_score", "ris"),
  c("Absolute error", "raem")
)
